### 2019-09-17 Thesis/promonads.tex
Random commit.

The purpose of this chapter is to shine some light on the definition of the \Mellies category, showing why it is natural to think about $[\X,\Set]$-enriched categories and why the \Mellies category may be considered analogous to the Kleisli category.

@@

\begin{definition}[\cite{Multicategories}]
  A \emph{multicategory} $\M$ is given by a set of objects $\text{Ob}(\M)$ whose elements are called \emph{objects} and, for each (possibly empty) list $a_1,\cdots,a_n$ of objects and each object $b$, a set
  \[
    \M_n(x_1,\cdots,x_n;y)
    \]
  whose elements are called the ($n$-ary) \emph{multimorphisms} $a_1,\cdots,a_n\to b$.

@@

  The composition and identity are subject to associativity and unitality conditions.
  Namely, let
  \begin{mathpar}
    \left(\mbox{\pbox{24pt}{$a_{pqr}$}} \suchthat \mbox{\pbox{80pt}{$p=1,\cdots,n$ \\ $q=1,\cdots,k_p$ \\ $r=1,\cdots, l_{pq}$}}\right)
    \and
    \left(\mbox{\pbox{24pt}{$b_{pq}$}} \suchthat \mbox{\pbox{80pt}{$p=1,\cdots,n$ \\ $q=1,\cdots,k_p$}}\right)
    \and
    (c_p\from p = 1,\cdots,n)
    \and
    d
  \end{mathpar}
  be collections of objects and let
  \begin{mathpar}
    f_{pq} \from a_{pq1},\cdots,a_{p,q,l_{pq}} \to b_{pq}
    \and
    g_p \from b_{p1},\cdots,b_{p,k_p} \to c_p
    \and
    d \from c_1,\cdots,c_n\to d
  \end{mathpar}
  be multimorphisms.
  Then we require that
  \begin{gather*}
    (((f_{11},\cdots,f_{1k_1});g_1),\cdots,((f_{n1},\cdots,f_{n,k_n});g_n));h\\
    =\\
    (f_{11},\cdots,f_{1k_1},\cdots,f_{n1},\cdots,f_{n,k_n});((g_1,\cdots,g_n);h)\,.
  \end{gather*}
  Furthermore, we require that if $f\from a_1,\cdots,a_n\to b$ is a multimorphism, then
  \begin{mathpar}
    (\id_{a_1},\cdots,\id_{a_n});f = f
    \and
    f = (f);\id_b\,.
  \end{mathpar}
\end{definition}

\begin{example}
  If $\C$ is an ordinary category, then $\C$ may be regarded as a multicategory $\hat{C}$ in which $\hat{C}_1(a;b)=\C(a,b)$ and $\hat{C}_n(a_1,\cdots,a_n;b)=\emptyset$ for $n\ne 1$.  
  At the same time, if $\M$ is a multicategory, then it has an \emph{underlying ordinary category} $\M_1$ whose morphisms are the morphisms in $\M$ with a single source object.
\end{example}
\begin{example}
  If $\M$ is a \emph{monoidal} category, then $\M$ may be regarded as a multicategory $\tilde{\M}$ with
  \begin{mathpar}
    \tilde{\M}_n(a_1,\cdots,a_n;b) = \M(a_1 \tensor \cdots \tensor a_n, b) \quad n\ge 1
    \and
    \tilde{\M}_0(;b) = \M(I, b)
  \end{mathpar}
  Since the tensor product is not necessarily strictly associative, it is not obvious exactly what we mean by $a_1 \tensor \cdots \tensor a_n$.
  In fact, it is enough to choose any one of the possible bracketings (e.g., to make $\blank\tensor\blank$ always associate to the right).

  Composition is then given by
  \begin{IEEEeqnarray*}{CCCCCC}
    & a_{11} \tensor \cdots \tensor a_{1k_1} & \tensor & \mathmakebox[4em]{\cdots} & \tensor & a_{n1} \tensor \cdots \tensor a_{nk_n} \\
    \xrightarrow{\mathmakebox[4em]{}} &
    (a_{11} \tensor \cdots \tensor a_{1k_1}) & \tensor & \mathmakebox[4em]{\cdots} & \tensor & (a_{n1} \tensor \cdots \tensor a_{nk_n}) \\
    \xrightarrow{\mathmakebox[4em]{f_1\tensor \cdots \tensor f_n}} &
    b_1 & \tensor & \mathmakebox[4em]{\cdots} & \tensor & b_n \\
    \xrightarrow{\mathmakebox[4em]{g}} &
    &&c\,,&&
  \end{IEEEeqnarray*}
  where the first arrow is induced from the normal monoidal coherences (exactly which ones depends on how we choose to interpret the iterated tensor product).
\end{example}

@@

We call a multicategory \emph{representable} if it isomorphic to a multicategory that arises from a monoidal category in this way.  
The next theorem gives a criterion for a multicategory to be representable.

\begin{theorem}[\cite{RepresentableMulticategories}]
  \label{TheRepresentableMulticategories}
  Let $\M$ be a multicategory and suppose that for each natural number $n$ and each sequence $a_1,\cdots,a_n$ of objects of $\M$ there is an object $\tensor \vec{a}$ and a multimorphism
  \[
    \pi_{\vec a} \from a_1,\cdots,a_n \to \tensor \vec a
    \]
  that is \emph{strongly universal} in the sense that if $b_1,\cdots b_k, c_1,\cdots,c_l$ are two (possibly empty) lists of objects, and $d$ is an object, then any multimorphism
  \[
    f \from b_1,\cdots,b_k,a_1,\cdots,a_n,c_1,\cdots,c_l \to d
    \]
  factors uniquely through $\pi_{\vec a}$; i.e., there is a unique morphism
  \[
    \hat{f} \from b_1,\cdots,b_k,\tensor\vec{a},c_1,\cdots,c_l \to d
    \]
  such that
  \[
    f=(\id_{b_1},\cdots,\id_{b_k},\pi_{\vec a},\id_{c_1},\cdots,\id_{c_l});\hat{f}\,.
    \]
  Define an operation $\blank\tensor\blank$ that sends objects $a,b$ of $\M$ to $a\tensor b = \tensor a,b$, and let $I$ be the object $\tensor\epsilon$, where $\epsilon$ is the empty list.  
  Then $\blank\tensor\blank$ and $I$ give rise to the multicategory structure on $\M$:
  \begin{itemize}
    \item $\blank\tensor\blank$ and $I$ are the monoidal product and unit of a monoidal category on $\M_1$, the underlying category of $\M$.
    \item For any sequence $a_1,\cdots a_n$ of objects of $\M$ there is a canonical isomorphism
      \[
        a_1 \tensor \cdots \tensor a_n \cong \tensor \vec a
        \]
      for any bracketing of the left hand side, and the associators and unitors in $\M_1$ are induced from these isomorphisms.
    \item The set of multimorphisms $a_1,\cdots,a_n \to b$ is in bijection with the set of morphisms $a_1\tensor\cdots\tensor a_n \to b$ for $n\ge1$, and the set of multimorphisms $\to b$ is in bijection with the set of morphisms $I \to b$, and these bijections commute with the multicategory composition in $\M$ and the composition in $\M_1$.
  \end{itemize}
\end{theorem}

\begin{definition}
  A \emph{symmetric multicategory} is a multicategory $\M$ together with an action of the symmetric group on the sets $\M_n(a_1,\cdots,a_n;b)$ that respects composition.  
  In other words, for each natural number $n$, each multimorphism $f\from a_1,\cdots,a_n\to b$ and each permutation $\sigma$ of $\{1,\cdots,n\}$ there is a multimorphism
  \[
    \sigma_* f \from a_{\sigma(1))},\cdots,a_{\sigma(n)} \to b
    \]
  such that if $(a_{ij}\from i=1,\cdots,n), (b_i\from i = 1,\cdots,n)$ are objects, 
  \begin{mathpar}
    f_i \from a_{i1},\cdots,a_{i,k_i} \to b_i
    \and
    g \from b_1,\cdots,b_n \to c
  \end{mathpar}
  are multimorphisms, $\sigma_i$ is a permutation of $\{1,\cdots,k_i\}$ and $\tau$ is a permutation of $\{1,\cdots,n\}$, then
  \[
    ({\sigma_1}_* f_q,\cdots,{\sigma_n}_*f_n);(\tau_*g) = (\tau*(\sigma_1,\cdots,\sigma_n))_*((f_1,\cdots,f_n);g)\,,
    \]
  where $\tau*(\sigma_1,\cdots,\sigma_n)$ is the permutation of
  \[
    \{(1,1),\cdots,(1,k_1),\cdots,(n,1),\cdots,(n,k_n)\}
    \]
  that sends $(i,j)$ to $(\tau(i),\sigma_i(j))$.

@@

\begin{definition}
  Let $\M,\N$ be multicategories.  
  The \emph{product multicategory} $\M\times\N$ has, as objects, pairs $(a,b)$, where $a$ is an object of $\M$ and $b$ an object of $\N$.  
  The multimorphisms are given by
  \begin{mathpar}
    (\M\times\N)_n((a_1,b_1),\cdots,(a_n,b_n);(c,d)) = \M_n(a_1,\cdots,a_n;c)\times\N_n(b_1,\cdots,b_n;d)\,.
  \end{mathpar}
  Composition and the identity are easily defined pointwise.
\end{definition}

@@

\begin{definition}
  Given multicategories $\M,\N$ and multifunctors 
  \[
    F,G\from \M \to \N\,,
    \]
  a \emph{multinatural transformation} $\phi\from F \Rightarrow G$ is given by morphisms $\phi_a \from F a \to G a$ for each object $a$ of $\M$, such that if $f\from a_1,\cdots a_n\to b$ is any morphism in $\M$, then the following diagram commutes.
  \[
    \begin{tikzcd}[column sep=36pt]
      Fa_1,\cdots, Fa_n \arrow[r, "{\phi_{a_1},\cdots,\phi_{a_n}}"] \arrow[d, "Ff"']
        & Ga_1,\cdots, Ga_n \arrow[d, "Gf"] \\
      Fb \arrow[r, "\phi_b"]
        & Gb
    \end{tikzcd}
    \]
\end{definition}

@@

\begin{definition}
  Let $\M,\N$ be multicategories, where $\M$ is symmetric.  
  Then the collection of multifunctors $\M\to\N$ forms a multicategory.  
  A multimorphism $F_1,\cdots,F_n\Rightarrow G$, where $F_1,\cdots,F_n,G$ are multifunctors $\M\to \N$, is given by a family
  \[
    \phi_a \from F_1(a),\cdots,F_n(a) \to G(a)
    \]
  such that for any multimorphism $f\from a_1,\cdots,a_m\to b$ in $\M$, the diagram
  \[
    \begin{tikzcd}[column sep=46pt]
      F_1(a_1),\cdots,F_n(a_1),\cdots,F_1(a_m),\cdots,F_n(a_m) \arrow[r, "{\phi_{a_1},\cdots,\phi_{a_m}}"] \arrow[d, "\sigma_*"']
        & G(a_1),\cdots,G(a_m) \arrow[dd, "Gf"] \\
      F_1(a_1),\cdots,F_1(a_m),\cdots,F_n(a_1),\cdots,F_n(a_m) \arrow[d, "{F_1f,\cdots,F_nf}"']
        & \\
      F_1(b),\cdots,F_n(b) \arrow[r, "\phi_b"]
        & G(b)
    \end{tikzcd}
    \]
  commutes, where $\sigma$ is the permutation of
  \[
    \{(1,1),\cdots,(n,1),\cdots,(1,m),\cdots,(n,m)\}
    \]
  that sends $(i,j)$ to $(j,i)$.
\end{definition}

@@

Note that a monoid in a multicategory $\M$ may also be defined to be a multifunctor $1 \to \M$ \cite[2.1.11]{Multicategories}.

@@

  In particular, a monoid in a multicategory $\M$ is the same thing as an $\M$-enriched category with a single object.

  Another equivalent definition of a monoid in a multicategory $\M$ is that it is a multifunctor from $1$ to $\M$, where $1$ is the unit monoidal category, considered as a multicategory.
\end{remark}

@@

  In the case $n=1$, this is the same thing as a $\V$-enriched functor from $\C_1$ to $\D$.
  We will use the word `functor' to refer to the more general multimorphisms between $\V$-enriched categories in the case that $\V$ is symmetric.
\end{definition}

@@

If $\V$ is a closed multicategory and $\C_1,\cdots,\C_n$ are $\V$-enriched categories, then a functor $\C_1,\cdots,\C_n \to \V$ is given by a map $\text{Ob}(\C_1)\times\cdots\times\text{Ob}(\C_n) \to \text{Ob}(\V)$ and, for each $a_i,b_i\in \text{Ob}(\C_i)$, a multimorphism
\[
  \C_1(a_1,b_1),\cdots,\C_n(a_n,b_n) \to \underline{\V}(F(a_1,\cdots,a_n),F(b_1,\cdots,b_n))
  \]
By the definition of a closed multicategory, this is equivalent to providing a multimorphism
\[
  F(a_1,\cdots,a_n),\C_1(a_1,b_1),\cdots,\C_n(a_n,b_n) \to F(b_1,\cdots,b_n)\,.
  \]
We will use the letter $p$ to refer to these multimorphisms and their various permutations.

@@

Let $F_1,\cdots,F_n,G \from \oppcat \C \times \C \to \V$ be $\V$-enriched profunctors $\C\pto \C$, where $\C$ is a $\V$-enriched category.

@@

We have only considered profunctors going from a category into itself.  
We might ask what structure is carried by more general profunctors enriched in a multicategory.
The answer is that they form an \emph{fc-multicategory} \cite{Multicategories}.

@@

\begin{proposition}[See, e.g., \cite{Promonad}]
  \label{PropPromonadsAreCategories}
  Let $\V$ be a symmetric closed multicategory.  
  Let $\C$ be a $\V$-enriched category.  
  Then a promonad $\D\from \C\pto \C$ is the same thing as a $\V$-enriched category $\D$ that admits an identity-on-objects functor $j\from \C \to \D$.
\end{proposition}
\begin{proof}
  This is a matter of unwrapping the definitions.

  Let $\D\from \C \pto \C$ be such a promonad.  
  So $\D$ is given by a functor $\D \from \oppcat \C,\C \to \V$, together with extranatural transformations
  \begin{mathpar}
    m_{a,b,c} \from \D(a,b),\D(b,c) \to \D(a,c)
    \and
    e_{a,b} \from \C(a,b) \to \D(a,b)
  \end{mathpar}
  such that the following diagrams commute (see Definition \ref{DefMonoidMulticategory}).
  \begin{mathpar}
    \begin{tikzcd}[column sep=12ex]
      \D(a,b),\D(b,c),\D(c,d) \arrow[r, "{m_{a,b,c},\id}"] \arrow[d, "{\id,m_{b,c,d}}"']
        & \D(a,c),\D(c,d) \arrow[d, "{m_{a,c,d}}"] \\
      \D(a,b),\D(b,d) \arrow[r, "{m_{a,b,d}}"]
        & \D(a,d)
    \end{tikzcd}
    \and
    \begin{tikzcd}
      \C(a,b),\D(b,c) \arrow[r, "p"] \arrow[d, "{e_{a,b},\id}"']
        & \D(a,c) \\
      \D(a,b),\D(b,c) \arrow[ur, "{m_{a,b,c}}"']
        &
    \end{tikzcd}
    \and
    \begin{tikzcd}
      \D(a,b),\C(b,c) \arrow[r, "p"] \arrow[d, "{\id,e_{a,b}}"']
        & \D(a,c) \\
      \D(a,b),\D(b,c) \arrow[ur, "{m_{a,b,c}}"']
        &
    \end{tikzcd}
  \end{mathpar}
  If we set $a=b$ in the second diagram and $b=c$ in the third, and compose with the identity multimorphisms $\eta$, then these are exactly the diagrams (see Definition \ref{DefEnrichedCategoryMulticategory}) for $\D$ to have the structure of a $\V$-enriched category on the collection of objects of $\C$!
  Moreover, $e_{a,b}$ gives us the enriched functor $\C\to \D$, which is the identity on objects and is the multimorphism $e_{a,b}$ on morphisms.

@@

\section{Monoids on functors are multifunctors}
It might seem strange that the objects of the multicategory of functors are ordinary functors, ignoring the monoidal structure of $\X$ and the multicategory structure of $\M$.  
One way to make sense of this fact is to note that an object of a category $\C$ is the same thing as a functor
\[
  1 \to \C\,.
  \]
In the same way, perhaps the correct way to think of an `element' of a multicategory is that it is a \emph{multifunctor}
\[
  1 \to \M\,;
  \]
i.e., a monoid in $\M$.

@@

We now come to our main result of the chapter.  
By way of motivation, consider the two ways of generalizing the notion of an internal monoid in $\Set$.

@@

The work we have done allows us to unify these into a single definition.  
From Proposition \ref{PropPromonadsAreCategories}, we know that a category with one object is the same thing as a monoid in the category $\Endoprof_\Set(*)$, where $*$ is the category with a single object and only an identity morphism.

@@

Our result is that these two ways of unifying the two generalization of a monoid in fact give the same result.  
The only ingredient we are missing is an appropriate change of base to move from ordinary $\Set$-enriched categories to $[\M,\Set]$-enriched categories.

\begin{definition}
  Let $\X$ be a monoidal category.  
  We have a multifunctor
  \[
    \X \to [\Set,\Set]
    \]
  given by
  \[
    x \mapsto \X(I,x) \times \blank\,.
    \]
  By Proposition \ref{PropPisani}, this may equivalently be given as a multifunctor
  \[
    \omega_\X\from\Set \to [\X,\Set]
    \]
  that sends a set $A$ to the functor
  \[
    \X(I,\blank)\times A\,.
    \]
\end{definition}

>>>>

The purpose of this short chapter is to shine some light on the definition of the \Mellies category for a parametric monad, showing why it is natural to think of it as being an analogue for the Kleisli category on a monad.

@@

\begin{definition}[\cite{Multicategories}]
  A \emph{multicategory} $\M$ is given by a set of objects $\text{Ob}(\M)$ whose elements are called \emph{objects} and, for each (possibly empty) list $a_1,\cdots,a_n$ of objects and each object $b$, a set
  \[
    \M_n(a_1,\cdots,a_n;b)
    \]
  whose elements are called the ($n$-ary) \emph{multimorphisms} $a_1,\cdots,a_n\to b$.

@@

  The composition and identity are subject to associativity and unitality conditions.
  Namely, let
  \begin{mathpar}
    \left(\mbox{\pbox{24pt}{$a_{pqr}$}} \suchthat \mbox{\pbox{80pt}{$p=1,\cdots,n$ \\ $q=1,\cdots,k_p$ \\ $r=1,\cdots, l_{pq}$}}\right)
    \and
    \left(\mbox{\pbox{24pt}{$b_{pq}$}} \suchthat \mbox{\pbox{80pt}{$p=1,\cdots,n$ \\ $q=1,\cdots,k_p$}}\right)
    \\
    (c_p\from p = 1,\cdots,n)
    \and
    d
  \end{mathpar}
  be collections of objects and let
  \begin{mathpar}
    f_{pq} \from a_{pq1},\cdots,a_{p,q,l_{pq}} \to b_{pq}
    \and
    g_p \from b_{p1},\cdots,b_{p,k_p} \to c_p
    \and
    h \from c_1,\cdots,c_n\to d
  \end{mathpar}
  be multimorphisms.
  Then we require that
  \begin{gather*}
    (((f_{11},\cdots,f_{1k_1});g_1),\cdots,((f_{n1},\cdots,f_{n,k_n});g_n));h\\
    =\\
    (f_{11},\cdots,f_{1k_1},\cdots,f_{n1},\cdots,f_{n,k_n});((g_1,\cdots,g_n);h)\,.
  \end{gather*}
  Furthermore, we require that if $f\from a_1,\cdots,a_n\to b$ is a multimorphism, then
  \begin{mathpar}
    (\id_{a_1},\cdots,\id_{a_n});f = f
    \and
    f = (f);\id_b\,.
  \end{mathpar}
\end{definition}

\begin{remark}
  We will use a slightly different form of commutative diagrams for multicategories, which should be fairly straightforward to understand.
  If, for example, we say that the following diagram commutes,
  \[
    \begin{tikzcd}[column sep=40pt]
      {a_1,\cdots,a_n} \arrow[r, "{f_1,\cdots,f_j}"] \arrow[d, "{g_1,\cdots,g_k}"']
        & {b_1,\cdots,b_j} \arrow[d, "h"] \\
      {c_1,\cdots,c_k} \arrow[r, "i"]
        & d
    \end{tikzcd}
    \]
  where the arities of $f_1,\cdots,f_j$ sum to $n$, as do the arities of $g_1,\cdots,g_k$, then we mean that the composite $(f_1,\cdots,f_k);h$ is equal to the composite $(g_1,\cdots,g_k);i$.
  We leave it to the reader to extend this to more complicated diagrams.
\end{remark}

\begin{example}
  If $\C$ is an ordinary category, then $\C$ may be regarded as a multicategory $\hat{C}$ in which $\hat{C}_1(a;b)=\C(a,b)$ and $\hat{C}_n(a_1,\cdots,a_n;b)=\emptyset$ for $n\ne 1$.  
  At the same time, if $\M$ is a multicategory, then it has an \emph{underlying ordinary category} $\M_1$ whose morphisms are the morphisms in $\M$ with a single source object.
\end{example}
\begin{example}
  If $\M$ is a \emph{monoidal} category, then $\M$ may be regarded as a multicategory $\tilde{\M}$ with
  \begin{mathpar}
    \tilde{\M}_n(a_1,\cdots,a_n;b) = \M(a_1 \tensor \cdots \tensor a_n, b) \quad n\ge 1
    \and
    \tilde{\M}_0(;b) = \M(I, b)
  \end{mathpar}
  If we're being careful, then we should note that the expression $a_1 \tensor \cdots \tensor a_n$ does not define a single object of $\M$, since the tensor product is not in general strictly associative.
  Since the tensor product is not necessarily strictly associative, it is not obvious exactly what we mean by $a_1 \tensor \cdots \tensor a_n$.
  It is enough to fix any one of the possible bracketings (e.g., to make $\blank\tensor\blank$ always associate to the right).

  Composition is then given by
  \begin{IEEEeqnarray*}{CCCCCC}
    & a_{11} \tensor \cdots \tensor a_{1k_1} & \tensor & \mathmakebox[4em]{\cdots} & \tensor & a_{n1} \tensor \cdots \tensor a_{nk_n} \\
    \xrightarrow{\mathmakebox[4em]{}} &
    (a_{11} \tensor \cdots \tensor a_{1k_1}) & \tensor & \mathmakebox[4em]{\cdots} & \tensor & (a_{n1} \tensor \cdots \tensor a_{nk_n}) \\
    \xrightarrow{\mathmakebox[4em]{f_1\tensor \cdots \tensor f_n}} &
    b_1 & \tensor & \mathmakebox[4em]{\cdots} & \tensor & b_n \\
    \xrightarrow{\mathmakebox[4em]{g}} &
    &&c\,,&&
  \end{IEEEeqnarray*}
  where the first arrow is induced from the normal monoidal coherences (exactly which ones depends on how we choose to interpret the iterated tensor product).
  \label{ExMonoidalCategoryAsMulticategory}
\end{example}

@@

We call a multicategory \emph{representable} if it isomorphic to a multicategory that arises from a monoidal category as in Example \ref{ExMonoidalCategoryAsMulticategory}.
The next theorem gives a criterion for a multicategory to be representable.

\begin{theorem}[\cite{RepresentableMulticategories}]
  \label{TheRepresentableMulticategories}
  Let $\M$ be a multicategory and suppose that for each natural number $n$ and each sequence $a_1,\cdots,a_n$ of objects of $\M$ there is an object $\tensor \vec{a}$ and a multimorphism
  \[
    \pi_{\vec a} \from a_1,\cdots,a_n \to \tensor \vec a\,.
    \]
  Suppose that the $\pi_{\vec a}$ are \emph{strongly universal} in the sense that if $b_1,\cdots b_k, c_1,\cdots,c_l$ are two (possibly empty) lists of objects, and $d$ is an object, then any multimorphism
  \[
    f \from b_1,\cdots,b_k,a_1,\cdots,a_n,c_1,\cdots,c_l \to d
    \]
  factors uniquely through $\pi_{\vec a}$; i.e., there is a unique morphism
  \[
    \hat{f} \from b_1,\cdots,b_k,\tensor\vec{a},c_1,\cdots,c_l \to d
    \]
  such that
  \[
    f=(\id_{b_1},\cdots,\id_{b_k},\pi_{\vec a},\id_{c_1},\cdots,\id_{c_l});\hat{f}\,.
    \]
  Given objects $a,b$ of $\M$, define $a\tensor b = \tensor a,b$, and let $I$ be the object $\tensor\epsilon$, where $\epsilon$ is the empty list.  
  Then the operation $\blank\tensor\blank$ and $I$ give rise to the multicategory structure on $\M$:
  \begin{itemize}
    \item $\blank\tensor\blank$ and $I$ are the monoidal product and unit of a monoidal category on $\M_1$, the underlying category of $\M$.
    \item For any sequence $a_1,\cdots a_n$ of objects of $\M$ there is a canonical isomorphism
      \[
        a_1 \tensor \cdots \tensor a_n \cong \tensor \vec a\,,
        \]
      for any bracketing of the left hand side, and the associators and unitors in $\M_1$ are induced from these isomorphisms.
    \item The set of multimorphisms $a_1,\cdots,a_n \to b$ is in bijection with the set of morphisms $a_1\tensor\cdots\tensor a_n \to b$ for $n\ge1$, and the set of multimorphisms $\to b$ is in bijection with the set of morphisms $I \to b$, and these bijections commute with the multicategory composition in $\M$ and the composition in $\M_1$.
  \end{itemize}
\end{theorem}

\begin{definition}
  A \emph{symmetric multicategory} is a multicategory $\M$ together with an action of the symmetric group on the sets $\M_n(a_1,\cdots,a_n;b)$ that respects composition.  
  In other words, for each natural number $n$, each multimorphism $f\from a_1,\cdots,a_n\to b$ and each permutation $\sigma$ of $\{1,\cdots,n\}$ there is a multimorphism
  \[
    \sigma_* f \from a_{\sigma(1))},\cdots,a_{\sigma(n)} \to b
    \]
  such that if $(a_{ij}\from i=1,\cdots,n), (b_i\from i = 1,\cdots,n)$ are objects, 
  \begin{mathpar}
    f_i \from a_{i1},\cdots,a_{i,k_i} \to b_i
    \and
    g \from b_1,\cdots,b_n \to c
  \end{mathpar}
  are multimorphisms, $\sigma_i$ is a permutation of $\{1,\cdots,k_i\}$, and $\tau$ is a permutation of $\{1,\cdots,n\}$, then
  \[
    ({\sigma_1}_* f_q,\cdots,{\sigma_n}_*f_n);(\tau_*g) = (\tau*(\sigma_1,\cdots,\sigma_n))_*((f_1,\cdots,f_n);g)\,,
    \]
  where $\tau*(\sigma_1,\cdots,\sigma_n)$ is the permutation of
  \[
    \{(1,1),\cdots,(1,k_1),\cdots,(n,1),\cdots,(n,k_n)\}
    \]
  that sends $(i,j)$ to $(\tau(i),\sigma_i(j))$.

@@

\begin{definition}
  Let $\M,\N$ be multicategories.  
  The \emph{product multicategory} $\M\times\N$ has, as objects, pairs $(a,b)$, where $a$ is an object of $\M$ and $b$ an object of $\N$.  
  The multimorphisms are given by
  \begin{mathpar}
    (\M\times\N)_n((a_1,b_1),\cdots,(a_n,b_n);(c,d)) = \M_n(a_1,\cdots,a_n;c)\times\N_n(b_1,\cdots,b_n;d)\,.
  \end{mathpar}
  Composition and the identity are similarly defined pointwise.
\end{definition}

@@

\begin{definition}
  Given multicategories $\M,\N$ and multifunctors 
  \[
    F,G\from \M \to \N\,,
    \]
  a \emph{multinatural transformation} $\phi\from F \Rightarrow G$ is given by morphisms 
  \[
    \phi_a \from F a \to G a
    \]
  for each object $a$ of $\M$, such that if $f\from a_1,\cdots a_n\to b$ is any morphism in $\M$, then the following diagram commutes.
  \[
    \begin{tikzcd}[column sep=36pt]
      Fa_1,\cdots, Fa_n \arrow[r, "{\phi_{a_1},\cdots,\phi_{a_n}}"] \arrow[d, "Ff"']
        & Ga_1,\cdots, Ga_n \arrow[d, "Gf"] \\
      Fb \arrow[r, "\phi_b"]
        & Gb
    \end{tikzcd}
    \]
\end{definition}

@@

\begin{definition}
  Let $\M,\N$ be multicategories, where $\M$ is symmetric.  
  Then the collection of multifunctors $\M\to\N$ forms a multicategory.  
  A multimorphism $F_1,\cdots,F_n\Rightarrow G$, where $F_1,\cdots,F_n,G$ are multifunctors $\M\to \N$, is given by a family
  \[
    \phi_a \from F_1(a),\cdots,F_n(a) \to G(a)
    \]
  such that for any multimorphism $f\from a_1,\cdots,a_m\to b$ in $\M$, the diagram
  \[
    \begin{tikzcd}[column sep=46pt]
      F_1(a_1),\cdots,F_n(a_1),\cdots,F_1(a_m),\cdots,F_n(a_m) \arrow[r, "{\phi_{a_1},\cdots,\phi_{a_m}}"] \arrow[d, "\sigma_*"']
        & G(a_1),\cdots,G(a_m) \arrow[dd, "Gf"] \\
      F_1(a_1),\cdots,F_1(a_m),\cdots,F_n(a_1),\cdots,F_n(a_m) \arrow[d, "{F_1f,\cdots,F_nf}"']
        & \\
      F_1(b),\cdots,F_n(b) \arrow[r, "\phi_b"]
        & G(b)
    \end{tikzcd}
    \]
  commutes, where $\sigma$ is the map
  \begin{mathpar}
    \{(1,1),\cdots,(n,1),\cdots,(1,m),\cdots,(n,m)\} \to \{(1,1),\cdots,(1,m),\cdots,(n,1),\cdots,(n,m)\}
  \end{mathpar}
  that sends $(i,j)$ to $(j,i)$, considered as a permutation of $\{1,\cdots,mn\}$.
\end{definition}

@@

Note that a monoid in a multicategory $\M$ may equivalently be defined as a multifunctor $1 \to \M$ \cite[2.1.11]{Multicategories}.

@@

  In particular, a monoid in a multicategory $\M$ is the same thing as an $\M$-enriched category with a single object.
\end{remark}

@@

  In the case $n=1$, this is the same thing as a $\V$-enriched functor from $\C_1$ to $\D$.
\end{definition}

@@

If $\V$ is a closed multicategory and $\C_1,\cdots,\C_n$ are $\V$-enriched categories, then a functor $\C_1,\cdots,\C_n \to \V$ is given by a map $\text{Ob}(\C_1)\times\cdots\times\text{Ob}(\C_n) \to \text{Ob}(\V)$ and, for each $a_i,b_i\in \text{Ob}(\C_i)$, a multimorphism
\[
  \C_1(a_1,b_1),\cdots,\C_n(a_n,b_n) \to \underline{\V}(F(a_1,\cdots,a_n),F(b_1,\cdots,b_n))
  \]
By the definition of a closed multicategory, this is equivalent to providing a multimorphism
\[
  F(a_1,\cdots,a_n),\C_1(a_1,b_1),\cdots,\C_n(a_n,b_n) \to F(b_1,\cdots,b_n)\,.
  \]
In what follows, we will denote these multimorphisms (and their various permutations) with the letter $p$.

@@

Let $F_1,\cdots,F_n,G \from \oppcat \C \times \C \to \V_1$ be $\V$-enriched profunctors $\C\pto \C$, where $\C$ is a $\V$-enriched category.

@@

We have only considered profunctors going from a category into itself.  
Profunctors in general form a structure called an \emph{fc-multicategory} \cite{Multicategories}, though we shall not be using this notion.

@@

\begin{proposition}[See, e.g., \cite{Promonad}]
  \label{PropPromonadsAreCategories}
  Let $\V$ be a symmetric closed multicategory.  
  Let $\C$ be a $\V$-enriched category.  
  Then a promonad $\D\from \C\pto \C$ is the same thing as a $\V$-enriched category $\D$ together with an identity-on-objects functor $j\from \C \to \D$.
\end{proposition}
\begin{proof}
  This is a matter of unwrapping the definitions.

  Let $\D\from \C \pto \C$ be such a promonad.  
  So $\D$ is given by a $\V$-enriched functor $\D \from \oppcat \C,\C \to \V_1$, together with extranatural transformations
  \begin{mathpar}
    m_{a,b,c} \from \D(a,b),\D(b,c) \to \D(a,c)
    \and
    e_{a,b} \from \C(a,b) \to \D(a,b)
  \end{mathpar}
  such that the following diagrams commute (see Definition \ref{DefMonoidMulticategory}).
  \begin{mathpar}
    \begin{tikzcd}[column sep=12ex]
      \D(a,b),\D(b,c),\D(c,d) \arrow[r, "{m_{a,b,c},\id}"] \arrow[d, "{\id,m_{b,c,d}}"']
        & \D(a,c),\D(c,d) \arrow[d, "{m_{a,c,d}}"] \\
      \D(a,b),\D(b,d) \arrow[r, "{m_{a,b,d}}"]
        & \D(a,d)
    \end{tikzcd}
    \and
    \begin{tikzcd}
      \C(a,b),\D(b,c) \arrow[r, "p"] \arrow[d, "{e_{a,b},\id}"']
        & \D(a,c) \\
      \D(a,b),\D(b,c) \arrow[ur, "{m_{a,b,c}}"']
        &
    \end{tikzcd}
    \and
    \begin{tikzcd}
      \D(a,b),\C(b,c) \arrow[r, "p"] \arrow[d, "{\id,e_{a,b}}"']
        & \D(a,c) \\
      \D(a,b),\D(b,c) \arrow[ur, "{m_{a,b,c}}"']
        &
    \end{tikzcd}
  \end{mathpar}
  If we set $a=b$ in the second diagram and $b=c$ in the third, and compose with the identity multimorphisms $\eta$, then these are exactly the diagrams (see Definition \ref{DefEnrichedCategoryMulticategory}) for $\D$ to have the structure of a $\V$-enriched category on the collection of objects of $\C$!

  Then the full versions of the second and third diagrams give us our desired enriched functor $\C\to \D$.  
  It is the identity on objects and is the multimorphism $e_{a,b}$ on morphisms.

@@

\section{Monoids on functors are multifunctors}
It might seem strange that the objects of the multicategory of functors are ordinary functors rather than multifunctors.  
We appear to have ignored the monoidal structure of $\X$ and the multicategory structure of $\M$.

One way to make sense of this fact is to note that an object of a category $\C$ is the same thing as a functor
\[
  1 \to \C\,.
  \]
In the same way, perhaps the correct way to think of an `element' of a multicategory is that it is a \emph{multifunctor}
\[
  1 \to \M\,;
  \]
i.e., a monoid in $\M$.

Then the following proposition tells us that the `elements' of $\X \to \M$ in this sense are the multifunctors.

@@

We now come to our main result of the chapter.  
We will approach it from an oblique perspective.  
First note the following two rather different generalizations of the notion of an internal monoid in $\Set$.

@@

We shall now attempt to unify these into a single grand unifying generalization of a monoid.
From Proposition \ref{PropPromonadsAreCategories}, we know that a category with one object is the same thing as a monoid in the category $\Endoprof_\Set(*)$, where $*$ is the category with a single object and only an identity morphism.

@@

Our main result will tell us that it doesn't actually matter which way round we choose: these two ways of unifying the two generalization of a monoid in fact give the same result.  
The only ingredient we are missing is an appropriate change of base to move from ordinary $\Set$-enriched categories to $[\M,\Set]$-enriched categories.

\begin{definition}
  Let $\X$ be a monoidal category.  
  We have a multifunctor
  \[
    \X \to [\Set,\Set]
    \]
  given by
  \[
    x \mapsto \X(I,x) \times \blank\,.
    \]
  By Proposition \ref{PropPisani}, this may equivalently be given as a multifunctor
  \[
    \partial_\X\from\Set \to [\X,\Set]
    \]
  that sends a set $A$ to the functor
  \[
    \X(I,\blank)\times A\,.
    \]
\end{definition}
